An Experimental Study of Sorting and Branch Prediction

### 2007-02-14 docs/branch_paper/paper.tex
Committing after a long time. IM logs added Minor updates to other stuff

\author{
PAUL BIGGAR\footnote[1]{Supported by the Irish Research Council for Science,
Engineering and Technology (IRCSET).}, NICHOLAS NASH\footnotemark[1], KEVIN
WILLIAMS\footnote[2]{Supported by the Irish Research Council for Science,
Engineering and Technology (IRCSET) and IBM.}, and DAVID GREGG \\University of
Dublin, Trinity College
}

@@

\category{E.5}{Data}{Files}[Sorting/Searching]
\category{C.1.1}{Computer Systems Organization}{Processor Architectures, Other
Architecture Styles}[Pipeline processors]
\terms{Algorithms, Experimentation, Measurement, Performance}
\keywords{Sorting, Branch Prediction, Pipeline Architectures, Caching}

>>>>

\author{
PAUL BIGGAR\footnote[1]{Supported by the Irish Research Council for Science,
Engineering and Technology (IRCSET).}, NICHOLAS NASH\footnotemark[1], KEVIN
WILLIAMS\footnote[2]{Supported by the Irish Research Council for Science,
Engineering and Technology (IRCSET) and IBM.}, and DAVID GREGG \\Trinity College
Dublin
}

@@

\category{E.5}{Data}{Files}[Sorting/Searching]
\category{C.1.1}{Computer Systems Organization}{Processor Architectures, Other
Architecture Styles}[Pipeline processors]
\terms{Algorithms, Experimentation, Measurement, Performance}
\keywords{Sorting, Branch Prediction, Pipeline Architectures}
